Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2015-05-20 doc/paper-lcr.tex
Keep Collett et al figs separate from future papers'

% Packages:
\input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}

@@

\date{to be submitted to MNRAS}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2012}

@@

High precision cosmological distance measurements towards individual objects
such as time delay gravitational lenses or type Ia supernovae are affected by
weak lensing perturbations by galaxies and groups along the line of sight. In
time delay gravitational lenses, ``external convergence,'' $\kappax$, can
dominate the uncertainty in the inferred distances and hence cosmological parameters.
 In this paper we attempt
to reconstruct $\kappax$, due to line of sight structure, using a simple halo
model.
%
We use mock catalogues from the Millennium Simulation, and calibrate and 
compare our reconstructed $\pr(\kappax)$ to ray-traced $\kappax$ ``truth''
values; taking into account realistic uncertainties on redshift and stellar
masses. \tom{We find that the reconstruction of $\kappax$ provides an improvement in
precision of $\sim$50\% over galaxy number counts.} 
%
We find that the lowest-$\kappax$ lines of sight have the best constrained 
$\pr(\kappax)$. In anticipation of future samples with thousands of lenses,
we find that selecting the third of the systems with the
highest precision $\kappax$ estimates gives a  sub-sample of unbiased time
delay distance measurements \phil{with (on average) just} 1\% uncertainty due
to line of sight external convergence effects. Photometric data alone are
sufficient to pre-select the best-constrained lines of sight, and can be done
before investment in light-curve monitoring. 
%
\phil{Conversely, we show that selecting lines of sight
with high external shear could, with the reconstruction model presented here,
induce biases of up to 1\% in time delay distance.} \new{We find that a major potential source of systematic error is uncertainty in the high mass end of the stellar mass-halo mass relation; this could introduce $\sim$2\% biases on the time-delay distance if completely ignored.} We suggest areas for the
improvement of this general analysis framework (including more sophisticated
treatment of high mass structures) that should allow yet more accurate
cosmological inferences to be made.

@@

The \MS results have been used to analyse real observations as well. 
\citet{SuyuEtal2010} selected \MS lines of sight by their apparent
galaxy over-density, in a 45 arcsec radius aperture down to $i < 24.5$,
to match the observed over-density towards the time delay lens
B1608$+$656 \citep{FassnachtEtal2011}.  The resulting distribution of
$\kappax$ values from the ray-tracing was taken to be an estimate of 
$\Pr(\kappax)$, which was then marginalised over when inferring the time
delay distance in this system. A similar procedure was used in \citet{SuyuEtal2012}.
In a companion paper to this one, Greene et al. (submitted) investigate
improvements to this method by weighting the galaxy counts by observables
including galaxy luminosity and perpendicular distance to the line of sight, again using the
\MS mock catalogues and their associated $\kappax$ values to construct
$\Pr(\kappax|\data)$. For the most over-dense lines of sight their
results  show a $\sim$20\% improvement over
number counts alone, but little improvement for less dense ones.

@@

\begin{figure*}
\includegraphics[width=\textwidth]{figs/viewofalightcone.eps}
\caption[magcut]{Four different views of a slightly over-dense \MS line
of sight, with a $\kappax$ of 0.03. 
{\it Top row, left:} The positions of galaxies projected on the sky. The area
of the circles is proportional to observed $i$-band flux; the brightest
object shown has an $i$ magnitude of 17.7. 
{\it Top row, centre:} The angular sizes of halos projected on the sky.
Red and blue regions lie within the NFW scale radius and virial radius
of each halo, respectively. There are essentially no empty lightcones. 
{\it Top row, right:} The individual $\kappax$ contributions of
each halo, assuming a \citet{BMO} truncated NFW 
profile and the \citet{Neto2007}
mass-concentration relation. Comparison of
this panel and the centre panel illustrates the relative importance of
proximity to the line of sight.
{\it Bottom:} A view along the redshift axis, showing only halos with
$|x|<0.3$ arcmin. The area of the points is proportional to each halo's
mass: the most massive halo shown has $1.6\times10^{12}\Msun$. The
optical axis is shown by the dashed line, while the dotted lines mark
the lens and source planes for a B1608-like strong lens.}
\label{fig:lightcone}
\end{figure*}

@@

We  take a large number of
calibration lines of sight from the \MS catalogues and generate a mock
stellar mass catalogue for each one. We then reconstruct each lightcone in the
same way as we would an observed field,
estimate $\pr(\kappah|\data)$, and extract its median. Accumulating
these median values $\kappah^{\rm med}$ and 
their corresponding true values of $\kappax$, we can form the 
conditional distribution $\pr(\kappax|\kappah^{\rm med})$. 
Then, to infer $\kappax$ from an observed photometric catalogue, we 
estimate $\pr(\kappah|\data)$ 
using the halo model, compute the median value 
$\kappa_{\rm h,obs}^{\rm med}$, and then use a modified
version of 
\Eref{eq:kappaconv} to infer $\kappax$: 
\bea
\Pr(\kappax|\kappah^{\rm med},\data) &=& \int \dee\kappah^{\rm med} 
   \Pr(\kappax|\kappah^{\rm med},\data) \Pr(\kappah^{\rm med}|\data) \notag \\
\label{eq:calkappaconv}   
\eea
\phil{This integral is trivial, since $\Pr(\kappah^{\rm med}|\data)$ is
a delta function centred on the median of the inferred PDF for $\kappah$.
However,}
because we only have a finite number of calibration lines of sight, we use all
calibration lines of sight with $\kappa_{\rm h,cal}^{\rm med} =
\kappah^{\rm med}\pm0.003$ to form $\Pr(\kappax|\kappah^{\rm
med},\data)$.
\comments{, with each calibration sightline weighted equally. PJM: why is
this? Surely one should weight by the value of the Gaussian function implied
by that ``$\pm 0.003$''?}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{figs/cornerplot.eps}
\caption[Biased?]{The conditional distribution of 
$\kappax$ given $\kappah$, in the case where  
we have perfect knowledge of halo mass and redshift.
$10^5$ reconstructed lines of
sight were used to make this plot. 
Solid (dashed) lines enclose 68\% (95\%) of the conditional probability.
$\kappah$ traces $\kappax$, but with a positive offset which arises from
$\kappah$ not accounting for any voids or dark structures.
At fixed $\kappah$ the scatter in $\kappax$ grows rapidly with $\kappah$.
\tom{The thin diagonal line follows $\kappax=\kappah$.}}
\label{fig:jointkh-k}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{figs/globaldist.eps}
\caption[magcut]{Recovering the global $\pr(\kappax)$ (shown in red). The
black curve shows a histogram of  inferred  $\kappax$ values from $10^{5}$
reconstructed lines of sight.  The reconstructions were performed given
perfect knowledge of halo mass and redshift -- in this case the reconstruction
recovers the correct convergence.}
\label{fig:globaldist}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\includegraphics[width=\textwidth]{figs/where_is_the_kappa.eps}
\caption[magcut]{Which objects dominate the external convergence for a line of
sight? From left to right, the three figures show the cumulative contribution
to the total convergence from individual halos ($\kappah$) as a function of
1) distance from the line of sight, 2) magnitude and 3) redshift.   In each
panel, the solid line is the median cumulative contribution over a large
sample of lines of sight, while dashed and dot-dashed show the ranges enclosing 68
and 95 percent of the lines of sight respectively. The source is at redshift 1.4.}
\label{fig:where}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{figs/radius_scatter.eps}
\caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
$\kappax$ as a function of the limiting radius of the halo
reconstruction. $\kappah$ has been shifted such that
$\left\langle\kappah\right\rangle=0$ \phil{to emulate the effect of the
eventual calibration}. 
The majority of the constraining power
comes from reconstructing halos within 2~arcmin of the line of sight.}
\label{fig:radcut}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{figs/mag_scatter.eps}
\caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
$\kappax$ as a function of the limiting $i$ band depth of the halo
reconstruction. $\kappah$ has been shifted such that
$\left\langle\kappah\right\rangle=0$ \phil{to emulate the effect of the
eventual calibration}. The majority of the constraining power
comes from reconstructing halos with magnitudes between $18<i<24$.}
\label{fig:magcut}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{figs/Width.eps}
\caption{The widths of the \infered PDFs $\pr(\kappax|\data)$ for
$10^5$ lines of sight, given different quality of data. 
Blue: spectroscopic redshift for every halo with $i<26$; 
Red: spectroscopic redshift for every halo with $i<23$, 
and every halo with $i<24$ within 1 arcminute, while all other objects just
have photometric redshifts;
Green: all the objects in the field have only photometric redshifts. The
vertical dot-dashed line marks the width of the global $\pr(\kappax)$ for all
lines of sight.}
\label{fig:reconwidths}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{figs/WidthvsHilbert.eps}
\caption{Width of the \infered PDF $\pr(\kappax|\data)$ as a function of 
the true convergence, $\kappaxtrue$, for two different data qualities. 
Black assumes only photometric redshifts for all objects,
while red assumes a campaign of targeted spectroscopy. The region between the
solid (dashed) lines contains 68\% (95\%) of lines-of-sight.}
\label{fig:widthsvsH}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure*}
\includegraphics[width=\textwidth]{figs/biasplots.eps}
\caption{Accuracy in $\kappax$ from combining samples of lenses.  These plots
show the expectation value of $\prod_{i=1}^N \pr_i(\kappax-\kappaxtrue|\data)$ --
deviations from zero represent biases. The solid, dashed and dotted lines
correspond to combinations of  20, 5 and 2 sightlines respectively. Black
lines show the results \infered from photometry alone, whilst red lines show
the results  from the same targeted spectroscopy campaign described in 
\Sref{sec:obsMstar+z:targetedspec}. The three panels correspond to samples of
sightlines selected in different ways. Left: randomly selected lines of
sight.  Centre: sightlines randomly selected from the 33\% of lines whose
P($\kappax$) is most tightly constrained by our model.  Right: lines of sight
with external shear of 0.05 or greater.}
\label{fig:biasplots}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{figs/SHAMbias.eps}
\caption{Systematic bias in $\kappax$ due to reconstructing lines of sight with the wrong stellar mass--halo mass relation. The real stellar masses were created using the relation of \citet{MosterEtal2010}, but the reconstruction and calibration assumes the relation of \citet{BehrooziEtal2010}.  These plots
show the expectation value of $\prod_{i=1}^N \pr_i(\kappax-\kappaxtrue|\data)$ --
deviations from zero represent biases. The solid, dashed and dotted lines
correspond to combinations of  20, 5 and 2 sightlines respectively. Black
lines show the results \infered from photometry alone, whilst red lines show
the results  from the same targeted spectroscopy campaign described in 
\Sref{sec:obsMstar+z:targetedspec}. The three panels correspond to samples of
sightlines selected in different ways. Left: randomly selected lines of
sight.  Centre: sightlines randomly selected from the 33\% of lines whose
P($\kappax$) is most tightly constrained by our model.  Right: lines of sight
with external shear of 0.05 or greater.}
\label{fig:SHAMbias}
\end{figure*}

@@

The reduction of $\pr(\kappah|\data)$ to just its median value, before using
it to look up the appropriate $\pr(\kappax)$ from the simulated sightline
ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
and Greene et al (submitted). The reconstruction method presented here can be
seen as the limiting case of the weightings explored by Greene et al: rather
than using weighted number counts in an aperture, we treat each galaxy
individually, and predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their
place. Given photometry alone, our reconstruction represents a $\sim$50\% improvement of
the precision compared the number counts used in \citet{SuyuEtal2010}. Greene et al.
made important progress for the most over-dense lines of sight; our
reconstructions are $\sim$30\% more precise than those of Greene et al.
The use of relative over-densities by Suyu et al. and Greene et al. may decrease 
their sensitivity to the choice of calibration simulation; this work's use of
absolute convergence may be less robust to changes in the calibration simulation.

@@

\section*{Acknowledgements}

TEC thanks Vasily Belokurov for supervision, guidance and suggestions.
We thank Risa Wechsler and Peter Behroozi 
for useful discussions and suggestions. We are grateful to the referee
for suggesting improvements to the original manuscript.
\input{acknowledgments.tex}

>>>>

% Packages:
%\input psfig.sty
\usepackage[totalwidth=500pt,totalheight=710pt]{geometry}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}

\graphicspath{{./}{figs-lcr/}}

@@

\date{Accepted for publication in MNRAS}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2012}

@@

High precision cosmological distance measurements towards individual objects
such as time delay gravitational lenses or type Ia supernovae are affected by
weak lensing perturbations by galaxies and groups along the line of sight. In
time delay gravitational lenses, ``external convergence,'' $\kappax$, can
dominate the uncertainty in the inferred distances and hence cosmological parameters.
 In this paper we attempt
to reconstruct $\kappax$, due to line of sight structure, using a simple halo
model.
%
We use mock catalogues from the Millennium Simulation, and calibrate and
compare our reconstructed $\pr(\kappax)$ to ray-traced $\kappax$ ``truth''
values; taking into account realistic uncertainties on redshift and stellar
masses. \tom{We find that the reconstruction of $\kappax$ provides an improvement in
precision of $\sim$50\% over galaxy number counts.}
%
We find that the lowest-$\kappax$ lines of sight have the best constrained
$\pr(\kappax)$. In anticipation of future samples with thousands of lenses,
we find that selecting the third of the systems with the
highest precision $\kappax$ estimates gives a  sub-sample of unbiased time
delay distance measurements \phil{with (on average) just} 1\% uncertainty due
to line of sight external convergence effects. Photometric data alone are
sufficient to pre-select the best-constrained lines of sight, and can be done
before investment in light-curve monitoring.
%
\phil{Conversely, we show that selecting lines of sight
with high external shear could, with the reconstruction model presented here,
induce biases of up to 1\% in time delay distance.} We find that a major potential source of systematic error is uncertainty in the high mass end of the stellar mass-halo mass relation; this could introduce $\sim$2\% biases on the time-delay distance if completely ignored. We suggest areas for the
improvement of this general analysis framework (including more sophisticated
treatment of high mass structures) that should allow yet more accurate
cosmological inferences to be made.

@@

The \MS results have been used to analyse real observations as well.
\citet{SuyuEtal2010} selected \MS lines of sight by their apparent
galaxy over-density, in a 45 arcsec radius aperture down to $i < 24.5$,
to match the observed over-density towards the time delay lens
B1608$+$656 \citep{FassnachtEtal2011}.  The resulting distribution of
$\kappax$ values from the ray-tracing was taken to be an estimate of
$\Pr(\kappax)$, which was then marginalised over when inferring the time
delay distance in this system. A similar procedure was used in \citet{SuyuEtal2012}.
In a companion paper to this one, \citet{Greene} investigate
improvements to this method by weighting the galaxy counts by observables
including galaxy luminosity and perpendicular distance to the line of sight, again using the
\MS mock catalogues and their associated $\kappax$ values to construct
$\Pr(\kappax|\data)$. For the most over-dense lines of sight their
results  show a $\sim$20\% improvement over
number counts alone, but little improvement for less dense ones.

\begin{figure*}
\includegraphics[width=\textwidth]{viewofalightcone.eps}
\caption[magcut]{Four different views of a slightly over-dense \MS line
of sight, with a $\kappax$ of 0.03.
{\it Top row, left:} The positions of galaxies projected on the sky. The area
of the circles is proportional to observed $i$-band flux; the brightest
object shown has an $i$ magnitude of 17.7.
{\it Top row, centre:} The angular sizes of halos projected on the sky.
Red and blue regions lie within the NFW scale radius and virial radius
of each halo, respectively. There are essentially no empty lightcones.
{\it Top row, right:} The individual $\kappax$ contributions of
each halo, assuming a \citet{BMO} truncated NFW
profile and the \citet{Neto2007}
mass-concentration relation. Comparison of
this panel and the centre panel illustrates the relative importance of
proximity to the line of sight.
{\it Bottom:} A view along the redshift axis, showing only halos with
$|x|<0.3$ arcmin. The area of the points is proportional to each halo's
mass: the most massive halo shown has $1.6\times10^{12}\Msun$. The
optical axis is shown by the dashed line, while the dotted lines mark
the lens and source planes for a B1608-like strong lens.}
\label{fig:lightcone}
\end{figure*}

@@

@@

We  take a large number of
calibration lines of sight from the \MS catalogues and generate a mock
stellar mass catalogue for each one. We then reconstruct each lightcone in the
same way as we would an observed field,
estimate $\pr(\kappah|\data)$, and extract its median. Accumulating
these median values $\kappah^{\rm med}$ and
their corresponding true values of $\kappax$, we can form the
conditional distribution $\pr(\kappax|\kappah^{\rm med})$.
Then, to infer $\kappax$ from an observed photometric catalogue, we
estimate $\pr(\kappah|\data)$
using the halo model, compute the median value
$\kappa_{\rm h,obs}^{\rm med}$, and then use a modified
version of
\Eref{eq:kappaconv} to infer $\kappax$:
\bea
\Pr(\kappax|\kappah^{\rm med},\data) &=& \int \dee\kappah^{\rm med}
   \Pr(\kappax|\kappah^{\rm med},\data) \Pr(\kappah^{\rm med}|\data) \notag \\
\label{eq:calkappaconv}
\eea
\phil{This integral is trivial, since $\Pr(\kappah^{\rm med}|\data)$ is
a delta function centred on the median of the inferred PDF for $\kappah$.
However,}
because we only have a finite number of calibration lines of sight, we use all
calibration lines of sight with $\kappa_{\rm h,cal}^{\rm med} =
\kappah^{\rm med}\pm0.003$ to form $\Pr(\kappax|\kappah^{\rm
med},\data)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{cornerplot.eps}
\caption[Biased?]{The conditional distribution of
$\kappax$ given $\kappah$, in the case where
we have perfect knowledge of halo mass and redshift.
$10^5$ reconstructed lines of
sight were used to make this plot.
Solid (dashed) lines enclose 68\% (95\%) of the conditional probability.
$\kappah$ traces $\kappax$, but with a positive offset which arises from
$\kappah$ not accounting for any voids or dark structures.
At fixed $\kappah$ the scatter in $\kappax$ grows rapidly with $\kappah$.
\tom{The thin diagonal line follows $\kappax=\kappah$.}}
\label{fig:jointkh-k}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{globaldist.eps}
\caption[magcut]{Recovering the global $\pr(\kappax)$ (shown in red). The
black curve shows a histogram of  inferred  $\kappax$ values from $10^{5}$
reconstructed lines of sight.  The reconstructions were performed given
perfect knowledge of halo mass and redshift -- in this case the reconstruction
recovers the correct convergence.}
\label{fig:globaldist}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\includegraphics[width=\textwidth]{where_is_the_kappa.eps}
\caption[magcut]{Which objects dominate the external convergence for a line of
sight? From left to right, the three figures show the cumulative contribution
to the total convergence from individual halos ($\kappah$) as a function of
1) distance from the line of sight, 2) magnitude and 3) redshift.   In each
panel, the solid line is the median cumulative contribution over a large
sample of lines of sight, while dashed and dot-dashed show the ranges enclosing 68
and 95 percent of the lines of sight respectively. The source is at redshift 1.4.}
\label{fig:where}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{radius_scatter.eps}
\caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
$\kappax$ as a function of the limiting radius of the halo
reconstruction. $\kappah$ has been shifted such that
$\left\langle\kappah\right\rangle=0$ \phil{to emulate the effect of the
eventual calibration}.
The majority of the constraining power
comes from reconstructing halos within 2~arcmin of the line of sight.}
\label{fig:radcut}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{mag_scatter.eps}
\caption[magcut]{The 16, 50 and 84th percentiles of $\kappah$ minus
$\kappax$ as a function of the limiting $i$ band depth of the halo
reconstruction. $\kappah$ has been shifted such that
$\left\langle\kappah\right\rangle=0$ \phil{to emulate the effect of the
eventual calibration}. The majority of the constraining power
comes from reconstructing halos with magnitudes between $18<i<24$.}
\label{fig:magcut}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{Width.eps}
\caption{The widths of the \infered PDFs $\pr(\kappax|\data)$ for
$10^5$ lines of sight, given different quality of data.
Blue: spectroscopic redshift for every halo with $i<26$;
Red: spectroscopic redshift for every halo with $i<23$,
and every halo with $i<24$ within 1 arcminute, while all other objects just
have photometric redshifts;
Green: all the objects in the field have only photometric redshifts. The
vertical dot-dashed line marks the width of the global $\pr(\kappax)$ for all
lines of sight.}
\label{fig:reconwidths}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\includegraphics[width=\columnwidth]{WidthvsHilbert.eps}
\caption{Width of the \infered PDF $\pr(\kappax|\data)$ as a function of
the true convergence, $\kappaxtrue$, for two different data qualities.
Black assumes only photometric redshifts for all objects,
while red assumes a campaign of targeted spectroscopy. The region between the
solid (dashed) lines contains 68\% (95\%) of lines-of-sight.}
\label{fig:widthsvsH}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure*}
\includegraphics[width=\textwidth]{biasplots.eps}
\caption{Accuracy in $\kappax$ from combining samples of lenses.  These plots
show the expectation value of $\prod_{i=1}^N \pr_i(\kappax-\kappaxtrue|\data)$ --
deviations from zero represent biases. The solid, dashed and dotted lines
correspond to combinations of  20, 5 and 2 sightlines respectively. Black
lines show the results \infered from photometry alone, whilst red lines show
the results  from the same targeted spectroscopy campaign described in
\Sref{sec:obsMstar+z:targetedspec}. The three panels correspond to samples of
sightlines selected in different ways. Left: randomly selected lines of
sight.  Centre: sightlines randomly selected from the 33\% of lines whose
P($\kappax$) is most tightly constrained by our model.  Right: lines of sight
with external shear of 0.05 or greater.}
\label{fig:biasplots}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{SHAMbias.eps}
\caption{Systematic bias in $\kappax$ due to reconstructing lines of sight with the wrong stellar mass--halo mass relation. The real stellar masses were created using the relation of \citet{MosterEtal2010}, but the reconstruction and calibration assumes the relation of \citet{BehrooziEtal2010}.  These plots
show the expectation value of $\prod_{i=1}^N \pr_i(\kappax-\kappaxtrue|\data)$ --
deviations from zero represent biases. The solid, dashed and dotted lines
correspond to combinations of  20, 5 and 2 sightlines respectively. Black
lines show the results \infered from photometry alone, whilst red lines show
the results  from the same targeted spectroscopy campaign described in
\Sref{sec:obsMstar+z:targetedspec}. The three panels correspond to samples of
sightlines selected in different ways. Left: randomly selected lines of
sight.  Centre: sightlines randomly selected from the 33\% of lines whose
P($\kappax$) is most tightly constrained by our model.  Right: lines of sight
with external shear of 0.05 or greater.}
\label{fig:SHAMbias}
\end{figure*}

@@

The reduction of $\pr(\kappah|\data)$ to just its median value, before using
it to look up the appropriate $\pr(\kappax)$ from the simulated sightline
ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
and \citet{Greene}. The reconstruction method presented here can be
seen as the limiting case of the weightings explored by Greene et al: rather
than using weighted number counts in an aperture, we treat each galaxy
individually, and predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their
place. Given photometry alone, our reconstruction represents a $\sim$50\% improvement of
the precision compared the number counts used in \citet{SuyuEtal2010}. Greene et al.
made important progress for the most over-dense lines of sight; our
reconstructions are $\sim$30\% more precise than those of Greene et al.
The use of relative over-densities by Suyu et al. and Greene et al. may decrease
their sensitivity to the choice of calibration simulation; this work's use of
absolute convergence may be less robust to changes in the calibration simulation.

@@

\section*{Acknowledgements}
TEC thanks Vasily Belokurov for supervision, guidance and suggestions.
We thank Risa Wechsler and Peter Behroozi
for useful discussions and suggestions. We are grateful to the referee
for suggesting improvements to the original manuscript.
%
TEC acknowledges support from STFC in the form of a research studentship.
%
PJM was given support by the Kavli Foundation and the Royal
Society, in the form of research fellowships.
%
% MWA \ldots
%
SH and RDB, and CDF, acknowledge support by the National Science Foundation
(NSF), grant numbers AST-0807458 and  AST-0909119, respectively.
%
SHS, ZG  and TT gratefully acknowledge support from the Packard Foundation in
the form of a Packard Research Fellowship to TT and from the
NSF grant AST-0642621.
%
LVEK acknowledges the support by an NWO-VIDI programme subsidy
(programme number 639.042.505).
%
% This research is supported in part by the National Science Foundation under
% Grant No. PHY99-07949.
%
The Millennium Simulation databases used in this paper and the web application
providing online access to them were constructed as part of the activities of
the German Astrophysical Virtual Observatory.

Our code for reconstructing lines of sight is publicly available at {https://github.com/drphilmarshall/Pangloss.}
